The supernova-regulated ISM - III. Magnetic fields in the multi-phase gas

### 2015-03-05 paper.tex

\documentclass[useAMS,usenatbib]{mn2e}
%FAG added header file to contain macros
\include{header}
%\usepackage{amsmath}
%\usepackage{bm}
%\usepackage{mathtools}
%\usepackage{graphicx,subfigure}
%\usepackage{caption}
%\usepackage{varioref}
%\usepackage{float}
%\restylefloat{table}
% If your system does not have the AMS fonts version 2.0 installed, then
% remove the useAMS option.
%
% useAMS allows you to obtain upright Greek characters.
% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
% this guide for further information.
%
% If you are using AMS 2.0 fonts, bold math letters/symbols are available
% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
% preferably \bmath).
%
% The usenatbib command allows the use of Patrick Daly's natbib.sty for
% cross-referencing.
%
% If you wish to typeset the paper in Times font (if you do not have the
% PostScript Type 1 Computer Modern fonts you will need to do this to get
% smoother fonts in a PDF file) then uncomment the next line
% \usepackage{Times}

@@

\section{Introduction}
%FAG rephrase
%The results presented in this paper are based on simulations of the multiphase interstellar medium (ISM) by Gent \textsl{et al} in \citep{GSFSM13} and \citep{GSSFM13}, %further referencing to Paper I & II needed here.
The results presented in this paper are based on simulations of the multiphase 
interstellar medium (ISM) reported in \citet{GSFSM13} and \citet{GSSFM13}, %further referencing to Paper I & II needed here.
subsequently referred to as \HD\, and \MHD, respectively.
%end FAG
%FAG rephrase
In particular we consider a model, identified as B1$\Omega$s in \MHD.
Supernova(SN)-driven turbulence is applied to ISM in a section of a spiral
galaxy differentially rotating, stratified about the galactic disk and subject
to, radiative cooling, photoelectric heating and other transport processes.
The rate and distribution of SN explosions, gravity and angular momentum are 
consistent with observational parameters for the solar neighbourhood.
A nano Gauss seed magnetic field is applied and amplified by dynamo until it
saturates with a mean magnetic stength of a few micro Gauss, remarkably 
consistent with observed estimates for the Milky Way.

@@

%focusing on the the B1$\Omega$s model of the ISM. This model features supernova(SN)-driven turbulence with gravity, differential rotation, SN explosions (SNe), radiative cooling, photoelectric heating and other transport processes, where the dynamo is in a kinematic statistically-steady state \citep{GSFSM13,GSSFM13}.\\
%end FAG
A snapshot of the ISM at approximately $t=1.4$ Gyr is used. Its characteristics, in terms of the fractional volumes of the phases, is representative of the steady-state phase of the dynamo. In addition, there are two potential SN remnants, which provide isolated structures of hot gas. This enhances the illustration of the effect that hot gas has on the mean magnetic field.

@@

\section{The mean magnetic field}
When considering the mean-field decomposition of the magnetic field, the notation used by \citep{GSSFM13} is adopted.
Volume averaging with a Gaussian kernel, $G_{l}(\bvec{x}-\bvec{x}')$ is used to decompose the magnetic field, $\bvec{B}$, into mean (large-scale), $\bvec{B}_{l}$ and random (small-scale), $\bvec{b}_{l}$, fields. The decomposition is given by 

@@

\bvec{B} = \bvec{B}_{l}+\bvec{b}_{l},\qquad \bvec{B}_{l} = \avg{B}. \label{decomp} 
Gaussian smoothing of the magnetic field with kernel size $l$ is represented by
\avg{B}&=\int_{V}\bvec{B}(\bvec{x}')G_{l}(\bvec{x}-\bvec{x}')d^{3}\bvec{x}',\\
G_{l}(\bvec{x})&=(2\pi l^2)^{-3/2}\exp[-\bvec{x}/(2l^2)],\nonumber
\label{gauss}
where $l\approx50$pc is half the integral scale of random motions \citep{GSSFM13}. This value is adopted for this paper based on the justification given in \citep{gent2}.  Preliminary analysis does not show significant sensitivity of the mean or random field to variations in $l$ within the range $0<l<100$pc. However, future work will consider analysis of isolated structures in the ISM. A more detailed analysis of length and correlation scales will be carried out. However, the current definition, $l=50$pc, is sufficient for the purposes of this paper. 
%\begin{table*}
 %\centering
 %\begin{minipage}{140mm}
  %\caption{Data on the RV Tauri stars detected by {\it IRAS}.}
  %\begin{tabular}{@{}llrrrrlrlr@{}}
  %\hline
  % Name     &            & \multicolumn{4}{c}{Flux density (Jy)%
 %\footnote{Observed by {\em IRAS}.}}\\
 % Variable & {\it IRAS} & 12$\,\umu$m & 25$\,\umu$m & 60$\,\umu$m
 %    & 100$\,\umu$m & Sp. & Period & Light- & $T_0\,(\rmn{K})$ \\
 %       &  &  &  &  &  & group & (d) & curve \\
 %       &  &  &  &  &  &       &     & type  \\
 %\hline
 %TW Cam & 04166$+$5719 & 8.27 & 5.62 & 1.82 & $<$1.73 & A & 85.6 & a & 555 \\
 %RV Tau & 04440$+$2605 & 22.53 & 18.08 & 6.40 & 2.52 & A & 78.9 & b & 460 \\
%\hline
%\end{tabular}
%\end{minipage}
%\end{table*}
%FAG added section from thesis -- to be edited
\include{mhdruns}
\section[]{Field lines of the magnetic field}
Field lines of the magnetic field give a qualitative description of the magnetic field in the ISM. We introduce sampling of physical variables along the field lines of the magnetic field, to obtain a quantitative description of the observables. Observables, such as entropy or pulsar RM measures \citep{SSFS02} are frequently used to derive other observables or statistics.  The use of sampling along field lines will enable the analysis of observables across many snapshots, whilst avoiding the use of time averages, which is not sensible for observables associated to a turbulent flow \citep{TL72}. For example, the wavelet transform methods used by Stepanov \textsl{et al} \citep{st02} are used to derive the Galactic magnetic field from pulsar RM data. Field lines of the Galactic magnetic field can be derived from this analysis and it can be further analysed using sampling along the field lines.\\
\boldmath
\subsection{Field line equation for a vector field, $\bvec{A}(\bvec{x})$}
\unboldmath
Given a vector field, $\bvec{A}(\bvec{x})$, in Cartesian coordinates, its field lines are described by
\frac{dx}{A_{x}}=\frac{dy}{A_{y}}=\frac{dz}{A_{z}}=ds,

@@

which are integrated using a $4^{th}$-order Runge-Kutta scheme. For discrete-valued $\bvec{A}(\bvec{x})$ interpolation is used to evaluate its components at positions, $\bvec{x}$, which do not lie on the data grid. 
\subsection{3D rendering of field lines of the mean magnetic field}
\hspace*{0cm} \includegraphics[width=\linewidth]{snapshot1.png}
\hspace*{0cm} \caption{3D rendering of the field lines of the mean magnetic field. The white lines are field lines seeded along a regular grid on the $xz$-plane at $y\approx-0.5$ kpc. 
\begin{figure}[h]
\includegraphics[width=\linewidth]{sline_vs_fld1.pdf}
\caption{PDFs of entropy (blue), $s$, log density (red), $\log(n)$, and log temperature (green), $\log(T)$, along field lines (solid) and straight lines (dashed).}
In Figure \vref{fig:fld_lines}, the white field lines have been seeded along the $xz$-axis at $y\approx-0.51$ kpc. The translucent gas inside the box is a representation of the log density, $\log(n)$, field. Density decreases from brighter to darker colours. Since the warm and hot phase represents approximately $\%99$ of the fractional volume of the ISM gas, it is only useful for visualising the characteristics of the field line within the warm and hot phases. We will present a preliminary result regarding the field lines within the cold phase in this paper. However, a more detailed discussion will be reported elsewhere. 
For descriptive purposes, the yellow shades of gas correspond to warm gas and the red shades correspond to the hot phase. We note that the field lines are generally aligned with the positive $y$-direction, especially in the warm phase and the field lines are smooth inside the warm gas. However, we notice significant differences in the characteristics of the field lines in the hot phase.\\ 
There is an isolated structure of hot gas (likely to be a SN remnant) in the (approximate) range $-0.8<z<-1.1$ kpc. The field lines in this region still traverse the computational domain in the positive $y$-direction. However, they are distorted and stretched in the positive $z$-direction in the region surrounding the hot gas.\\  
Similarly, in the range $0.7<z<1.1$ kpc, there is a larger structure of hot gas, which spans the $xy$-plane. This structure appears to be part of rising hot gas, which is leaving the computational domain. As it leaves, it elongates the magnetic field lines until they are no longer connected inside the domain. Consequently, the the field lines are approximately perpendicular to the $y$-axis, where the stretching of the field lines occur due to the hot phase. (NEED TO CHECK WHETHER THE MAGNETIC FIELD ENERGY IS STRONGER IN THESE REGIONS COMPARED WITH THE STRAIGHT LINES!)
\subsection{A Test: Comparison of probability density functions (PDFs) along field lines with PDFs along straight lines}
\noindent Figure \vref{fig:pdfs_mean} shows the probability density functions (PDFs) of entropy, log density and log temperature sampled along field lines (solid lines) and straight lines (dashed lines). The PDFs for log density and log temperature suggest that the PDFs have similar overall behaviour, which is most likely due to their alignment in the $y$-direction. This is reassuring since the choice of aligning the straight lines in the $y$-direction was to avoid introducing uncharacteristic behaviour into the comparison. The straight lines have the orientation of the field lines, without the sensitivity to phases.\\
We now consider the PDFs entropy along the field lines and straight lines in Figure \ref{fig:pdfs_mean}. These PDFs are more rich in information. Firstly, we observe similar peaks in the region $1.66<s<10.365$, which corresponds to the warm phase. This agrees with Figure \vref{fig:fld_lines} in that the field lines do not seem sensitive to the warm phase. \\
\begin{table}[H]
 %\begin{minipage}{180mm}
  \caption{Respective probabilities of finding the field and straight in the cold, warm and hot phases.}
  \label{table:mean_probs}
 % \begin{tabular*}{@{}c c c @{}}{\linewidth}{@{\extracolsep{\fill}}p{0.3\linewidth}p{0.3\linewidth}p{0.3\linewidth}@{}}
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}p{0.3\linewidth}p{0.3\linewidth}p{0.3\linewidth}@{}}
  \hline
   Probability& Field lines& Straight lines \\
 \hline
\\
$\mathcal P(\text{cold phase})$&$8.384\cdot10^{-5}$ &$7.818\cdot10^{-4}$  \\
   $\mathcal P(\text{warm phase})$& $0.6577$&$0.8865$   \\
   $\mathcal P(\text{hot phase})$&$0.3422$ & $0.1127$    \\
\hline
\end{tabular*}
%\end{minipage}
\end{table}
\noindent We observe a sharp peak for the PDF of entropy along the field line, centred at $s\approx27\cdot10^8$ erg g$^{-1}$ K$^{-1}$, which is inside the hot phase. A similar peak is not observed for the PDF of entropy along the straight line. This can be explained by the field lines being stretched by the hot gas and thus traversing the hot phase for a higher proportion of their length than the straight lines, which are not affected by stretching. We formulate probabilities of traversing each phase for the field lines and straight lines from their PDFs. The probabilities are expressed as,

@@

The probabilities of traversing the phases, for the field lines and straight lines, are given in \ref{table:mean_probs}. We observe that the probabilities of the straight lines traversing each phase closely match the fractional volumes of the phases, as expected; lines that are not sensitive should traverse each phase with probability proportional to the fractional volume. 
On the other hand, the probability of a field line traversing the hot phase is significantly higher than that of a straight line, which reiterates the effect of the stretching of field lines by the phase. The probability of a field line traversing the warm phase is lower than that of a straight line. However, this is a direct consequence of the distortion of the magnetic field by the hot phase. We note that the probability of a field line traversing the cold phase is lower than that of a straight line by an order of magnitude. This could constitute a preliminary indication that the field lines avoid the cold phase. As noted earlier, the characteristics of the magnetic field in the cold phase will be explored in greater detail elsewhere.  
\subsection{Field lines of the total and random magnetic field}
We use Equation \eqref{f_lines_eqn} to construct field lines for the total and random magnetic field using the same method as for field lines of the mean magnetic field. Sampling along these lines is used to obtain the PDF of  entropy, as seen in the previous section for the mean magnetic field. PDFs of log density and log temperature have been omitted, since the PDF of entropy contains sufficient detail to understand the characteristics of the field lines. The comparison with PDFs along straight lines are only relevant for field lines of the mean magnetic field. This section focuses on the comparison of PDFs along the total, mean and random magnetic field. 

@@

\includegraphics[width=\linewidth]{decomp_pdf_overall.pdf}
\caption{PDFs of $s$ along field lines of the mean (blue solid), total (red solid) and random (green solid) fields. The boundaries of between the cold and warm phases (black dashed) and between the warm and hot phases (black solid) are indicated.}

@@

Figure \vref{fig:tot_pdfs} shows these PDFs. FIrstly, we note that all of the PDFs are clustered in the warm and hot phases. However, this is inextricably linked to the fractional volumes of the phases. It is difficult to discuss whether avoidance of the cold phase by the field line is also a contributing factor.\\
We concentrate on the warm and hot phases. The PDF for the total field is similar to that of the mean field in the warm phase. They both have a smooth distribution, even though the PDF of the total appears to be slightly more skewed. In the hot phase, the PDF for the total field is smooth. However, The PDF of the mean field peaks sharply, at approximately $s=27\cdot10^8$ erg g$^{-1}$ K$^{-1}$. Even though the PDF for the total field is smooth, its local maxima is close to this value of $s$. A similarly sharp peak is observed in this region for the PDF of the random field. This could suggest that $s=27\cdot10^8$ erg g$^{-1}$ K$^{-1}$ is a characteristic entropy associated with the hot phase for this snapshot. \\

>>>>

\documentclass[useAMS,usenatbib]{mn2e}
%FAG added header file to contain macros
\include{header}
% If your system does not have the AMS fonts version 2.0 installed, then
% remove the useAMS option.
%
% useAMS allows you to obtain upright Greek characters.
% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
% this guide for further information.
%
% If you are using AMS 2.0 fonts, bold math letters/symbols are available
% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
% preferably \bmath).
%
% The usenatbib command allows the use of Patrick Daly's natbib.sty for
% cross-referencing.
%
% If you wish to typeset the paper in Times font (if you do not have the
% PostScript Type 1 Computer Modern fonts you will need to do this to get
% smoother fonts in a PDF file) then uncomment the next line
% \usepackage{Times}

@@

%-----------------------------------------------------------------------------
\section{Introduction}
%-----------------------------------------------------------------------------

FAG -- notes -- include Beck, Fletcher, Berkhuijsen observations of magnetic 
fields \citep{2013AN....334..548B, MNR18065} and observation/estimates of multiphase structure \citep{dummy}
\citep{CS74,M077}

%FAG rephrase
%The results presented in this paper are based on simulations of the multiphase interstellar medium (ISM) by Gent \textsl{et al} in \citep{GSFSM13} and \citep{GSSFM13}, %further referencing to Paper I & II needed here.
The results presented in this paper are based on simulations of the multiphase 
interstellar medium (ISM) reported in \citet{GSFSM13} and \citet{GSSFM13}, %further referencing to Paper I & II needed here.
subsequently referred to as \HD\, and \MHD, respectively.
%end FAG
%FAG rephrase
%CCE rephrase based on comments & suggestions by AS
In particular we consider a model, identified as B1$\Omega$s in \MHD.
Supernova(SN)-driven turbulence is applied to ISM in a section of a spiral
galaxy differentially rotating, stratified about the galactic disk and subject
to, radiative cooling \citep{Sarazin87,Wolfire95}, photoelectric heating
\citep{Wolfire95} and other transport processes.
The rate and distribution of SN explosions, gravity \citep{Kuijken89} and 
angular momentum are consistent with observational parameters for the solar
neighbourhood \citep{F01}.
A nano Gauss seed magnetic field is applied and amplified by dynamo until it
saturates with a mean magnetic stength of a few micro Gauss, remarkably 
consistent with observed estimates for the Milky Way \citep{dummy}.
%end CCE rephrase

@@

%focusing on the the B1$\Omega$s model of the ISM. This model features supernova(SN)-driven turbulence with gravity, differential rotation, SN explosions (SNe), radiative cooling, photoelectric heating and other transport processes, where the dynamo is in a kinematic statistically-steady state \citep{GSFSM13,GSSFM13}.\\
%end FAG
Twelve snapshots in the time range, $1.40\Gyr<t<1.67\Gyr$ are used. 
This time range corresponds to the steady-state phase of the system. 
In addition, there are two potential SN remnants, which provide isolated 
structures of hot gas. 
In addition, a snapshot at $t=1.4$ Gyr is also presented 
(Figure \ref{fig:fld_lines}) to illustrate the effect of the hot phase on 
the magnetic field.

@@

%-----------------------------------------------------------------------------
\section{The mean magnetic field}
%-----------------------------------------------------------------------------

%FAG rephrase
The decomposition of the magnetic field into mean and fluctuating (random) 
field follows \MHD.
%end FAG
%When considering the mean-field decomposition of the magnetic field, the notation used by \citep{GSSFM13} is adopted.
Volume averaging with a Gaussian kernel, $G_{l}(\bvec{x}-\bvec{x}')$ is used to decompose the magnetic field, $\bvec{B}$, into mean (large-scale), $\bvec{B}_{l}$ and random (small-scale), $\bvec{b}_{l}$, fields. The decomposition is given by 
\begin{equation}
\bvec{B} = \bvec{B}_{l}+\bvec{b}_{l},\qquad \bvec{B}_{l} = \avg{B}. \label{decomp} 
\end{equation}
Gaussian smoothing of the magnetic field with kernel size $l$ is represented by
\begin{align}
\avg{B}&=\int_{V}\bvec{B}(\bvec{x}')G_{l}(\bvec{x}-\bvec{x}')d^{3}\bvec{x}',\\
G_{l}(\bvec{x})&=(2\pi l^2)^{-3/2}\exp[-\bvec{x}/(2l^2)],\nonumber
\label{gauss}
\end{align} 
where $l\approx50$pc is half the integral scale of random motions \citep{GSSFM13}. This value is adopted for this paper based on the justification given in \citep{gent2}.  Preliminary analysis does not show significant sensitivity of the mean or random field to variations in $l$ within the range $0<l<100$pc. However, future work will consider analysis of isolated structures in the ISM. A more detailed analysis of length and correlation scales will be carried out. However, the current definition, $l=50$pc, is sufficient for the purposes of this paper. 
%\begin{table*}
 %\centering
 %\begin{minipage}{140mm}
  %\caption{Data on the RV Tauri stars detected by {\it IRAS}.}
  %\begin{tabular}{@{}llrrrrlrlr@{}}
  %\hline
  % Name     &            & \multicolumn{4}{c}{Flux density (Jy)%
 %\footnote{Observed by {\em IRAS}.}}\\
 % Variable & {\it IRAS} & 12$\,\umu$m & 25$\,\umu$m & 60$\,\umu$m
 %    & 100$\,\umu$m & Sp. & Period & Light- & $T_0\,(\rmn{K})$ \\
 %       &  &  &  &  &  & group & (d) & curve \\
 %       &  &  &  &  &  &       &     & type  \\
 %\hline
 %TW Cam & 04166$+$5719 & 8.27 & 5.62 & 1.82 & $<$1.73 & A & 85.6 & a & 555 \\
 %RV Tau & 04440$+$2605 & 22.53 & 18.08 & 6.40 & 2.52 & A & 78.9 & b & 460 \\
%\hline
%\end{tabular}
%\end{minipage}
%\end{table*}

%-----------------------------------------------------------------------------
%FAG added section from thesis -- to be edited
\input{mhdruns}
%end FAG
%-----------------------------------------------------------------------------

%-----------------------------------------------------------------------------
\section[]{Magnetic field lines}
%-----------------------------------------------------------------------------

Magnetic field lines give a qualitative description of the magnetic field in 
the ISM. 
We introduce sampling of physical variables along the field lines of the 
magnetic field, to obtain a quantitative description of the observables. 
Observables, such as entropy or pulsar RM measures \citep{SSFS02} are 
frequently used to derive other observables or statistics.  
The use of sampling along field lines will enable the analysis of observables 
across many snapshots, whilst avoiding the use of time averages, which is not 
sensible for observables associated to a turbulent flow \citep{TL72}. 
For example, wavelet transform methods are used by \citet{st02}, to derive the
Galactic magnetic field from pulsar RM data. 
Field lines of the Galactic magnetic field can be derived from this analysis 
and it can be further analysed using sampling along the field lines.

%\boldmath
%-----------------------------------------------------------------------------
\subsection{Field line equation for a vector field, $\bvec{B}(\bvec{x})$}
%-----------------------------------------------------------------------------
%\unboldmath

Given a vector field, $\bvec{B}(\bvec{x})$, in Cartesian coordinates, its field lines are described by

@@

\frac{dx}{B_{x}}=\frac{dy}{B_{y}}=\frac{dz}{B_{z}}=ds,

@@

which are integrated using a $4^{th}$-order Runge-Kutta scheme. For discrete-valued $\bvec{B}(\bvec{x})$ interpolation is used to evaluate its components at positions, $\bvec{x}$, which do not lie on the data grid.
\subsubsection{Sampling observables along field lines}
Having obtained a set of field lines, observables are sampled on each point along the field lines. The multi-phase structure of the ISM gas and the turbulent flows within the ISM gas suggest that the data obtained from sampling these observables along the field lines will not necessarily have a simple, parametric statistical description. Consequently, the use of histograms to represent the data could be misleading where the convergence of the histograms pose a non-trivial problem. We circumvent this issue by using Gaussian kernel density estimation, which provides a non-parametric method for obtaining a probability density function (PDF) of the sampled observable data. Preliminary work included observables such as density and temperature. However, we have found that PDFs of entropy provide sufficient information. Thus, we restrict our attention to PDFs of specific entropy, $s$, sampled along field lines. This PDF is expressed as $\mathcal{P}(s)$. The definition of the multi-phase structure is given below in terms of specific entropy, $s$, with units erg g$^{-1}$ K$^{-1}$:
\text{Cold phase:}\qquad s\leq3.7\cdot10^8,\\
\text{Warm phase:}\qquad 3.7\cdot10^8<s\leq23.2\cdot10^8,\\
\text{Hot phase:}\qquad s>23.2\cdot10^8.\\
\label{phase_defns}
We define the probability of finding a point along a field line in each of the phases using the phase definitions. These are

@@

We make extensive use of PDFs of sampled variables, both graphically and to make specific statements about the characteristics of the magnetic fields in the ISM.
\subsubsection{Analysis of the sensitivity of magnetic field lines to the multi-phase structure}
In addition, similar samples can be taken from snapshots which are statistically independent in time. If the seeding for the field line calculations are carried out identically for each snapshot, a physically meaningful ensemble average is obtained. The twelve snapshots used in this paper are statistically independent in time and are taken from the statistically-steady phase of the system.
\subsubsection{Correlation analysis of magnetic field lines using PDFs}
We also use PDFs to analyse the correlation lengths of the magnetic fields in the multi-phase. We calculate the maximum displacement of the field lines from their seed point, $r$, and their maximum displacement along the $x$, $y$ and $z$ axes, $r_x$, $r_y$ and $r_z$, respectively. PDFs of these quantities are calculated using kernel density estimation. As an example, we consider some field line, $L_i$, with seed point, $\bvec{x}_0\equiv(x_0,y_0,z_0)$. The field line must have a minimum and maximum displacement from the seed point, which is a direct consequence of the solenoidality of the magnetic field. The maximum displacement occurs at some $\bvec{x}_{max}$ along $L_i$ such that $r=|\bvec{x_{max}}-\bvec{x}|$. The maximum displacements along the axes are described by $r_x = x_{max}-x_0$, $r_y = y_{max}-y_0$, $r_z = z_{max}-z_0$. We calculate typical length scales for each of these displacements, using the mean of the random variable. For example, for $r$, we use
C = \int_{r_{min}}^{r_{max}}r\mathcal{P}(r)dr,
where $r_{min}$ and $r_{max}$ are the minimum and maximum values of $r$ observed across all snapshots and $\mathcal{P}(r)$ is the PDF of $r$. The typical length scales $C_x$, $C_y$, $C_z$ along the $x$, $y$ and $z$ axes, respectively, are calculated using similar expressions. 
\subsection{The phase that hosts the magnetic field}
The mean magnetic field is considered first, to explore the large-scale characteristics of the magnetic field, having extracted the small-scale fluctuations with Gaussian volume averaging.  Intuition suggests that the mean magnetic field will prefer to stay in the warm phase, which provides a less hostile environment for the magnetic field than the transonic, compressible turbulence of the hot phase. As discussed in Section \label{sect:3BB}, the magnetic field is very strong and well-aligned with the azimuthal ($y$) direction in the $|z|<0.6$kpc region, where the warm phase dominates. In the $0.6<|z|<1.0$kpc region, the hot phase dominates. Consequently, the magnetic field is not well aligned and much weaker than the magnetic field in the warm phase. The the turbulent flows in the $0.6<|z|<1.0$kpc region will have the highest kinetic energies throughout the ISM (CALCULATE THESE AVERAGE VALUES). Conversely, the magnetic field is very weak in the hot phase (Fig.~\ref{fig:b2dent}). Subsequently, the kinetic energy of the flows should be at least of a comparable order to the magnetic field energy in this region.  We expect this to cause distortions in the magnetic field (CCE: REFERENCE TAYLOR HERE). The lack of alignment and weakness of the magnetic field in this region (Fig. \ref{fig:b3box}) imply that the magnetic field is sensitive to the hot phase. The characteristics of the magnetic field lines further clarify the effect of the hot phase on the magnetic field.
\subsubsection{Distortion of the mean magnetic field lines in the hot phase}
In Figure \ref{fig:fld_lines}, data from the snapshot at $t=1.4$ Gyr are used. The white field lines have been seeded along the $xz$-axis at $y=-0.51$ kpc. The translucent gas inside the box is a representation of the log density field. Density decreases from brighter to darker colours. Since the warm and hot phase represents approximately $\%99$ of the volume of the ISM gas, it is only useful for visualising the characteristics of the field line within the warm and hot phases.

%-----------------------------------------------------------------------------
\subsection{3D rendering of field lines of the mean magnetic field}
%-----------------------------------------------------------------------------

\begin{figure*}
  \vspace{0cm}
  \centering
\hspace*{0cm} \includegraphics[width=\linewidth]{snapshot1.png}
\hspace*{0cm} \caption{3D rendering of the field lines of the mean magnetic field. The white lines are field lines seeded along a regular grid on the $xz$-plane at $y\approx-0.5$ kpc. 
  \label{fig:fld_lines}}
  \end{figure*}
\begin{figure}
\centering
\includegraphics[width=\linewidth]{sline_vs_fld1.pdf}
\caption{PDFs of entropy (blue), $s$, log density (red), $\log(n)$, and log temperature (green), $\log(T)$, along field lines (solid) and straight lines (dashed).}
\label{fig:pdfs_mean}
\end{figure}
%-----------------------------------------------------------------------------

In Figure \vref{fig:fld_lines}, the white field lines have been seeded along 
the $xz$-axis at $y\approx-0.51$ kpc. 
The translucent gas inside the box is a representation of the log density, 
$\log(n)$, field. 
Density decreases from brighter to darker colours. 
Since the warm and hot phase represents approximately $\%99$ of the fractional
volume of the ISM gas, it is only useful for visualising the characteristics 
of the field line within the warm and hot phases. 
We will present a preliminary result regarding the field lines within the 
cold phase in this paper. 
However, a more detailed discussion will be reported elsewhere. 
For descriptive purposes, the yellow shades of gas correspond to warm gas and 
the red shades correspond to the hot phase. 
We note that the field lines are generally aligned with the positive 
$y$-direction, especially in the warm phase and the field lines are smooth 
inside the warm gas. 
However, we notice significant differences in the characteristics of the 
field lines in the hot phase.

There is an isolated structure of hot gas (likely to be a SN remnant) in the
(approximate) range $-0.8<z<-1.1$ kpc. 
The field lines in this region still traverse the computational domain in the 
positive $y$-direction. 
However, they are distorted and stretched in the positive $z$-direction in 
the region surrounding the hot gas.

Similarly, in the range $0.7<z<1.1$ kpc, there is a larger structure of hot 
gas, which spans the $xy$-plane. 
This structure appears to be part of rising hot gas, which is leaving the 
computational domain. As it leaves, it elongates the magnetic field lines 
until they are no longer connected inside the domain. 
Consequently, the the field lines are approximately perpendicular to the 
$y$-axis, where the magnetic field lines are strecthed and distorted by the 
hot phase.

\noindent 
Figure \ref{fig:pdfs_mean} shows the probability density functions (PDFs) of 
entropy sampled along field lines (solid lines) and straight lines (dashed
lines) for the snapshot at $t=1.4$ Gyr. 
The PDFs show that the magnetic field lines and straight lines have similar 
overall behaviour, due to their alignment in the $y$-direction. 
The alignment of the straight lines in the azimuthal ($y$) direction was 
chosen to ensure that the straight lines are representative of the general 
alignment of the magnetic field, without introducing any sensitivity to the 
multi-phase structure.

We now consider the PDFs entropy along the field lines and straight lines 
in Figure \ref{fig:pdfs_mean}. 
Firstly, we observe similar peaks in the warm phase. 
This agrees with Figure \ref{fig:fld_lines} in that the field lines are 
not sensitive to the warm phase. 
The probabilities of traversing the phases, for the field lines and straight 
lines, are given in Table \ref{table:mean_probs}. 
We observe that the probabilities of the straight lines traversing each phase
closely match the fractional volumes of the phases, as expected; lines that 
are not phase-sensitive should traverse each phase with probability 
proportional to the fractional volume.

On the other hand, the probability of a field line traversing the hot phase
is significantly higher than that of a straight line, which reiterates the 
effect of the stretching of field lines by the phase. 
The probability of a field line traversing the warm phase is lower than that 
of a straight line. 
However, this is a direct consequence of the distortion of the magnetic field 
by the hot phase. 
The probability of the field line crossing the cold phase is much smaller than
$1\%$ for both field lines and straight lines. 
The fractional volume of the cold phase is typically very small. 
Consequently, a different approach is required to analyse the characteristics
of the magnetic field in the cold phase.

Overall, the magnetic field lines traverse the ISM in the azimuthal direction. 
This trend is observed clearly in the warm phase, where the magnetic field is 
not distorted by the flows of the ISM gas. 
Since the field lines represent lines of magnetic flux density, the 
distortion of the magnetic field lines by the hot phase explains the weakness 
of the magnetic field observed in the hot phase. 
The stretching of the magnetic field lines effectively wrap the field lines 
around the hot gas, which increases the field line density on the boundary 
of the hot and warm gas. 
Consequently, field lines do not pass through the hot gas 
(Fig.~\ref{fig:fld_lines}) and we observe that the magnetic field in the hot 
phase is very weak and lacking alignment. 
This strongly suggests that the magnetic field resides in the warm phase.    
%-----------------------------------------------------------------------------
\begin{table}
 \centering
 %\begin{minipage}{180mm}
  \caption{Respective probabilities of finding the field and straight in the cold, warm and hot phases.}
  \label{table:mean_probs}
 % \begin{tabular*}{@{}c c c @{}}{\linewidth}{@{\extracolsep{\fill}}p{0.3\linewidth}p{0.3\linewidth}p{0.3\linewidth}@{}}
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}p{0.3\linewidth}p{0.3\linewidth}p{0.3\linewidth}@{}}
  \hline
   Probability& Mean field lines& Straight lines \\
 \hline
\\
$\mathcal P(\text{cold phase})$&$\ll1\%$ &$\ll1\%$  \\
   $\mathcal P(\text{warm phase})$& $0.79$&$0.89$   \\
   $\mathcal P(\text{hot phase})$&$0.20$ & $0.11$    \\
\hline
\end{tabular*}
%\end{minipage}
\end{table}
%-----------------------------------------------------------------------------

%-----------------------------------------------------------------------------
\footnote{CAN: please add snapshot1new.png to the repository}
\hspace*{0cm} \includegraphics[scale=0.35]{fig/snapshot1.png}
%\hspace*{0cm} \includegraphics[scale=0.35]{fig/snapshot1new.png}
\hspace*{0cm} \caption{3D rendering of the field lines of the mean magnetic field at $t = 1.4$ Gyr. The white lines are field lines seeded along a regular grid on the $xz$-plane at $y=-0.51$ kpc. 
%-----------------------------------------------------------------------------

@@

\includegraphics[width=\linewidth]{fig/snapshot1.png}
%\includegraphics[width=\linewidth]{snapshot0_entropy.pdf}
\caption{PDFs of entropy sampled along field lines (blue) and straight lines (red).}
\footnote{CAN: please add snapshot0\_entropy.pdf to the repository} 
%-----------------------------------------------------------------------------
%-----------------------------------------------------------------------------
\subsection{The mean and random magnetic fields}
%-----------------------------------------------------------------------------
We use Equation \eqref{f_lines_eqn} to construct field lines for the random magnetic field using the same method as for field lines of the mean magnetic field. Sampling along these lines (across twelve snapshots) is used to obtain the PDF of entropy, as seen in the previous section for the mean magnetic field. 
\subsubsection{Ensemble averaged characteristics of the mean and random magnetic field lines }
Fig. \ref{fig:tot_pdfs} shows the PDF of entropy sampled along the mean field (blue solid). We note that the probability density in the cold phase is still negligible, despite larger data set used. In the warm phase, the PDF peaks at a similar value to that of entropy in Fig. \ref{fig:pdfs_mean}. However, we do not observe a sharp peak for entropy of the mean field in the hot phase in Fig. \ref{fig:tot_pdfs}. Nonethless, the probability density of entropy in the hot phase is consistently higher than the PDF of entropy for straight lines. The difference can be attributed to the significant stretching of the mean magnetic field in the hot phase in the snapshot at $t=1.4$ Gyr and the larger data set used for the ensemble average. Stretching of the mean field occurs in other snapshots, albeit to a less severe extent. Severe stretching of the magnetic field occurs where a SN remnant is present. 
 %%CCE edit - delete
%The comparison with PDFs along straight lines are only relevant for field lines of the mean magnetic field. This section focuses on the comparison of PDFs along the total, mean and random magnetic field. 
%%End CCE edit
\footnote{CAN: please add ent\_pdfs.pdf and prob\_corrs\_all.pdf to the repository} 
\subfigure[]{\includegraphics[width=0.49\linewidth]{fig/snapshot1.png}}
%\subfigure[]{\includegraphics[width=0.49\linewidth]{ent_pdfs.pdf}}
%\subfigure[]{\includegraphics[width=0.49\linewidth]{prob_corrs_all.pdf}}
\caption{\textbf{(a)} PDFs of $s$ along field lines of the mean (blue solid), total (red solid) and random (green solid) magnetic fields. The boundaries of between the cold and warm phases (black dashed) and between the warm and hot phases (black solid) are indicated. \textbf{(b)} PDFs of maximum distance from the seed point of field lines for the mean (blue solid), total (green solid) and random (red solid) magnetic fields.}

@@

As discussed in the previous section, the field lines of the mean magnetic field has a greater probability density in the hot phase than the straight lines, which indicates that the stretching of the field lines by hot gas is a general characteristic. The PDF of entropy sampled along mean magnetic field lines is also more skewed towards higher entropies in the warm phase than the PDF of entropy sampled along straight lines, which suggests the mean magnetic field prefers to stay in hot, low density regions of the warm phase.\\
In contrast, we observe that the PDF of entropy sampled along the random magnetic field lines is skewed towards cooler, denser regions of the warm phase. Further, the probability density of the PDF for the random field is consistently lower than that of the straight lines, in the hot phase. This is unexpected given the random (generally unaligned and weak) nature of the magnetic field in the hot phase. %(CHECK MAGNETIC FIELD ENERGIES - Is random magnetic field higher energy? If so, might not be as suscpetible to distortion by high energy turbulent flows. )
